---
output: 
  pdf_document:
    citation_package: natbib
    keep_tex: false
    latex_engine: pdflatex
    template: "svm-latex-memo.tex"
fontfamily: times
fontsize: 12pt
geometry: margin=0.8in
header-includes:
   - \linespread{0.90}

from: Adam Storch
to: Files
subject: "`r paste0(as.numeric(format(Sys.Date(), '%Y'))-1, ' Willamette River spring Chinook Run and ',as.numeric(format(Sys.Date(), '%Y')), ' forecast')`"
date: "`r format(as.Date('2012-08-13'), '%d %B %Y')`"
memorandum: true
graphics: true
width: 0.2
logoposition: left
logo: "odfwLogo.v.2.png"
---
```{r echo=FALSE}
harv_rt_form = function(x) ifelse(is.na(x),"", sprintf("%.1f%%", x*100))
harv_rt_formSm = function(x) ifelse(is.na(x),"", sprintf("%.2f%%", x*100))
int_form = function(x) ifelse(is.na(x),"", formatC(x,digits = 0, format = "f", big.mark = ","))
int_deci_form = function(x) ifelse(is.na(x),"", formatC(x,digits = 1, format = "f", big.mark = ","))
year_form = function(x) ifelse(is.na(x),"", formatC(x,digits = 0, format = "f"))
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(flextable)
library(ggplot2)
library(magrittr)
library(openxlsx)
library(officer)
library(webshot)
library(officedown)
library(data.table)
library(berryFunctions)
library(scales)
```

```{r echo=FALSE}
### define current run year (value has to be entered manually)
curr_year <- 2022

### load data files
#### define file path (make sure: Tools->Global Options...->R Markdown->
#### Evaluate chunks in directory = "Project")
inPath <- 'Input/~Input Data/'
predPath <- 'Output/Predictions/'

#### input data
load(
  file = paste(
    inPath,
    curr_year,
    "willClackInpData.rda",
    sep=""
  )
)

#### new (curr_year+1) predictions
curr.will.predns <- readRDS(
  paste(
    predPath,
    curr_year+1,
    'willComb.pred.out.rds',
    sep = ""
  )
)

#### prior years' (curr_year) predictions
prior.will.predns <- readRDS(
  paste(
    predPath,
    curr_year,
    'willComb.pred.out.rds',
    sep = ""
  )
)

#### new (curr_year+1) predictions
curr.clack.predns <- readRDS(
  paste(
    predPath,
    curr_year+1,
    'clack.pred.out.rds',
    sep = ""
  )
)

#### prior years' (curr_year) predictions
prior.clack.predns <- readRDS(
  paste(
    predPath,
    curr_year,
    'clack.pred.out.rds',
    sep = ""
  )
)
     
```
  
## Summary of `r as.numeric(format(Sys.Date(), '%Y'))-1` Willamette River spring Chinook return

### Subsection Test

The total Willamette River spring Chinook return to the Columbia River mouth during `r as.numeric(format(Sys.Date(), '%Y'))-1` is estimated to be `r format(willChsRet.dat[nrow(willChsRet.dat)-1,3] + willChsRet.dat[nrow(willChsRet.dat)-2,4] + willChsRet.dat[nrow(willChsRet.dat)-3,5] + willChsRet.dat[nrow(willChsRet.dat)-4,6], big.mark = ",")` fish (Table 1).  An estimated `r format(willChsHWprop.dat[nrow(willChsHWprop.dat),5], big.mark = ",")` of these fish were unmarked (~`r percent(willChsHWprop.dat[nrow(willChsHWprop.dat),4])`).  The `r as.numeric(format(Sys.Date(), '%Y'))-1` total reconstructed return was approximately `r percent(as.numeric(willChsRet.dat[nrow(willChsRet.dat)-1,3] + willChsRet.dat[nrow(willChsRet.dat)-2,4] + willChsRet.dat[nrow(willChsRet.dat)-3,5] + willChsRet.dat[nrow(willChsRet.dat)-4,6])/as.numeric(prior.predns[6,2]))` of forecast.  The Clackamas River component was approximately `r percent(as.numeric(clackChsRet.dat[nrow(clackChsRet.dat),6])/as.numeric(prior.predns[6,2]))` 151% of forecast, with `r format(clackChsRet.dat[nrow(clackChsRet.dat),6], big.mark = ",")` spring Chinook returning to the Clackamas River compared to 4,247 (95% credible interval: 2,479–7,291) fish expected.

The total return of adipose-fin-marked hatchery fish to the Columbia River mouth in 2022 is estimated to be 46,589, compared to 39,090 fish expected.  Counts at the Willamette Falls fishway indicate that 31,937 fin-marked hatchery fish and 6,692 unmarked fish passed the fish ladder.  The full reconstruction of the 2022 return is shown in Table 2.